---
output: github_document
editor_options: 
  chunk_output_type: console
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
) 

r_latest <- max(package_version(unique(rcheology::rcheology$Rversion)))
```

# rcheology

[![Travis build status](https://travis-ci.org/hughjonesd/rcheology.svg?branch=master)](https://travis-ci.org/hughjonesd/rcheology) 
[![AppVeyor build status](https://ci.appveyor.com/api/projects/status/github/hughjonesd/rcheology?branch=master&svg=true)](https://ci.appveyor.com/project/hughjonesd/rcheology)
[![CRAN status](https://www.r-pkg.org/badges/version/rcheology)](https://cran.r-project.org/package=rcheology)
[![CRAN downloads](https://cranlogs.r-pkg.org/badges/rcheology)](https://cran.r-project.org/package=rcheology) 
 
A data package which lists every command in base R packages since R version `r min(package_version(unique(rcheology::rcheology$Rversion)))`.

The latest R version covered is `r r_latest`.

You can view the data online in a [Shiny app](https://hughjonesd.shinyapps.io/rcheology/).

## Installing

From CRAN:

```{r, eval = FALSE}
install.packages('rcheology')
```

```{r, child = "data-where-from.Rmd"}
```

## Do it yourself

* Install docker.
* `./control build` builds the images. Or get them from https://hub.docker.com/r/dash2/rcheology/.
* `./control run` runs the images to build/install R and extract data
* `./control gather` gets CSV files from the containers
* `./control write` puts CSV files into a data frame and stores it in the package

## The data


```{r}
library(rcheology)
data("rcheology")

head(rcheology)
```
 
Latest changes:

```{r}

suppressPackageStartupMessages(library(dplyr))

r_penultimate <- sort(package_version(unique(rcheology::rcheology$Rversion)), 
      decreasing = TRUE)
r_penultimate <- r_penultimate[2]

r_latest_obj <- rcheology %>% filter(Rversion == r_latest)
r_penult_obj <- rcheology %>% filter(Rversion == r_penultimate)

r_introduced <- anti_join(r_latest_obj, r_penult_obj, by = c("package", "name"))

r_introduced
```
 
Base functions over time:

```{r}
library(ggplot2)

rvs <- rcheology$Rversion     %>% 
      unique()                %>% 
      as.package_version()    %>% 
      sort() %>% 
      as.character()

major_rvs <- grep(".0$", rvs, value = TRUE)
major_rv_dates <- Rversions$date[Rversions$Rversion %in% major_rvs]
major_rvs <- gsub("\\.0$", "", major_rvs)

rch_dates <- rcheology %>% left_join(Rversions, by = "Rversion")
ggplot(rch_dates, aes(date, group = package, fill = package), colour = NA) + 
      stat_count(geom = "area") + 
      theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 8)) + 
      # ggthemes::scale_fill_gdocs() +
      scale_x_date(breaks  = major_rv_dates, labels = major_rvs) + 
      xlab("Version") + ylab("Function count") + 
      theme(legend.position = "top")


```

An alternative view:

```{r, fig.height = 8, out.height="1000px"}


ggplot(rch_dates, aes(date, fill = "orange")) + 
      stat_count(geom = "area") + 
      scale_x_date(breaks  = major_rv_dates, labels = major_rvs) + 
      theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 8)) + 
      xlab("Version") + ylab("Function count") + 
      facet_wrap(~package, scales = "free_y", ncol = 2) +
      theme(legend.position = "none") 
```
