---
output: github_document
editor_options: 
  chunk_output_type: inline
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# rcheology

[![Travis build status](https://travis-ci.org/hughjonesd/rcheology.svg?branch=master)](https://travis-ci.org/hughjonesd/rcheology) 
[![AppVeyor build status](https://ci.appveyor.com/api/projects/status/github/hughjonesd/rcheology?branch=master&svg=true)](https://ci.appveyor.com/project/hughjonesd/rcheology)
[![CRAN status](https://www.r-pkg.org/badges/version/rcheology)](https://cran.r-project.org/package=rcheology)

A data package which lists every command in base R packages since R version 2.0.0.

The latest R version covered is `r max(package_version(unique(rcheology::rcheology$Rversion)))`.

## Installing

```{r, eval = FALSE}
install.packages("remotes") # if you need to
remotes::install_github("hughjonesd/rcheology")
```

## Where the data comes from

Versions 3.0.1 and up are installed from the [CRAN apt repositories for Ubuntu Trusty Tahr](https://cran.r-project.org/bin/linux/ubuntu/trusty/). Version 3.5.0 and up use a 
[special repository](https://cran.r-project.org/bin/linux/ubuntu/trusty-cran35/).

Versions 2.5.1 to 3.0.0 are built from source on [Ubuntu Lucid Lynx](https://hub.docker.com/r/yamamuteki/ubuntu-lucid-i386/).

Versions 2.0.0 to 2.4.1 are built from source on [Debian Sarge](https://hub.docker.com/r/debian/eol/).

Results are found from running `ls` on all installed packages from a minimal installation.
Recommended packages are not included.

The `Rversions` data frame lists versions of R and release dates.

## Do it yourself

* Install docker
* `./control build` builds the images. Or get them from https://hub.docker.com/r/dash2/rcheology/.
* `./control run` runs the images to build/install R and extract data
* `./control gather` gets CSV files from the containers
* `./control write` puts CSV files into a data frame and stores it in the package

## The data

You can view the data online in a [Shiny app](https://hughjonesd.shinyapps.io/rcheology/).

```{r}
library(rcheology)
data("rcheology")

head(rcheology)
```

Base functions over time:

```{r}
library(ggplot2)
suppressPackageStartupMessages(library(dplyr))

rvs <- rcheology$Rversion     %>% 
      unique()                %>% 
      as.package_version()    %>% 
      sort() %>% 
      as.character()

major_rvs <- grep(".0$", rvs, value = TRUE)
major_rv_dates <- Rversions$date[Rversions$Rversion %in% major_rvs]

rch_dates <- rcheology %>% left_join(Rversions, by = "Rversion")
ggplot(rch_dates, aes(date, group = package, fill= package), colour = NA) + 
      stat_count(geom = "area") + 
      theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 8)) + 
      ggthemes::scale_fill_gdocs() +
      scale_x_date(breaks  = major_rv_dates, labels = major_rvs) + 
      xlab("Version") + ylab("Function count")
   
```

