---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# rcheology

A data package which lists every command in base R packages since R version 3.0.2.

## Installing

```{r, eval = FALSE}
install.packages("remotes") # if you need to
remotes::install_github("hughjonesd/rcheology")
```

## The data

```{r}
library(rcheology)
data("rcheology")

head(rcheology)
```

Packages over time
```{r}
xtabs(~ Rversion + package, data = rcheology)

```

## Running it yourself

* Install docker
* Build the image from `Dockerfile` with `docker build -t rcheology .`
* Run the image with `docker run rcheology`.
* It will download and install multiple versions of R on the container.
* Check the container name with `docker container ls` (or `ls -a` after the process is finished).
* Source `gather-data.R` to get data out of the container and into a CSV file.

