---
output: github_document
editor_options: 
  chunk_output_type: inline
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# rcheology

A data package which lists every command in base R packages since R version 2.0.0.

## Installing

```{r, eval = FALSE}
install.packages("remotes") # if you need to
remotes::install_github("hughjonesd/rcheology")
```

## Running it yourself

* Install docker
* `./control build` builds the images
* `./control run` runs the images to build/install R and extract data
* `./control gather` gets CSV files from the containers
* `./control write` puts CSV files into a data frame and stores it in the package

## The data

You can view the data online in a [Shiny app](https://hughjonesd.shinyapps.io/rcheology/).

```{r}
library(rcheology)
data("rcheology")

head(rcheology)
```

Base functions over time:

```{r}
library(ggplot2)
library(dplyr)

rvs <- rcheology$Rversion     %>% 
      unique()                %>% 
      as.package_version()    %>% 
      sort() %>% 
      as.character()

major_rvs <- grep(".0$", rvs, value = TRUE)
      
ggplot(rcheology, aes(Rversion, group = package, fill= package), colour = NA) + 
      stat_count(geom = "area") + 
      theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 8)) + 
      ggthemes::scale_fill_gdocs() +
      scale_x_discrete(limits  = rvs, breaks = major_rvs)
   
```

